---
title: "Some changepoint simulation"
author: "P. Fearnhead & G. Rigaill"
date: "15 février 2018"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary & Parameters

Here we explore some segmentation approaches and their performances on various datasets.
This is a draft.

```{r}
mc.cores=4
nb_simu_per_dataset=100
```

## Simulated datasets

We will test a number of segmentation approaches on various simulated datasets.
For each datasets we need to define a number of parameters 

- a name
- the mean of each vector (mu)
- the changes (bkp)
- the length of each segment (Lg)
- the standard deviation (sigma)
- the true number of changes (Ktrue)
- the signal (signal)

We store the parameter of each dataset in a list. Here is 
the code for our first dataset.

```{r dataset1, fig.height=5}
Simu <- list()
isimu <- 0

isimu <- isimu+1
Simu[[isimu]] <- list()
Simu[[isimu]]$Name <- "Dataset-1, K=12, n=2048"
Simu[[isimu]]$bkp  <- c(0, c(205, 267, 308, 472, 512, 820, 902, 1332, 1557, 
                                  1598, 1659) - 1, 2048)
Simu[[isimu]]$Lg <- diff(Simu[[isimu]]$bkp)
Simu[[isimu]]$mu <- c(0, 14.64, -3.66, 7.32, -7.32, 10.98, -4.39, 
                      3.29, 19.03,7.68, 15.37, 0)
Simu[[isimu]]$sigma=10; 
Simu[[isimu]]$signal <- rep(Simu[[isimu]]$mu, Simu[[isimu]]$Lg); 
Simu[[isimu]]$Ktrue <- sum(diff(Simu[[isimu]]$signal)!=0)+1

```

The defintion of all other datasets is in the "StatDatasets.R" file.
We source them below.

```{r statdatasets}
source("StatDatasets.R")
```

### An example profile for each dataset

We know simulate and plot a profile for each dataset.

```{r plot_dataset, fig.width=4, fig.height=3.4}

## 
type.errors <- c("Gauss", "Stud-10")
rSimu <- function(sim, type.error="Gauss"){
  if(type.error == "Gauss"){
    x <- rep(sim$mu, sim$Lg) + rnorm(sum(sim$Lg), sd=sim$sigma)
  }
  if(type.error =="Stud-10"){
    dfree <- 10
    x <- rep(sim$mu, sim$Lg) 
    x <- x + rt(n=length(x), df=dfree)*sim$sigma
  }
  return(x)
}

for(sim in Simu){
  x <- rSimu(sim, type.error="Gauss")
  plot(x, pch=20, col="blue", lty=2, main=sim$Name, cex=0.3, xlab="", ylab="")
  abline(v=sim$bkp, lty=2)
  segments(x0=sim$bkp[-length(sim$bkp)], y0=sim$mu, sim$bkp[-1], col="red", lwd=2)
}


```

### Larger datasets 

Finally we consider a few more datasets extending the previous one by
multiplying the length of each segment by $\alpha$ and dividing the standard 
deviation by $\sqrt(\alpha)$. We use $\alpha=3$ and $\alpha=10$
This is done in the following script.

```{r extended_datasets}
one_Extend_Simu_Lg <- function(sim, alpha){
  sim$bkp    <- sim$bkp*alpha
  sim$Lg     <- diff(sim$bkp)
  sim$sigma  <- sim$sigma*sqrt(alpha)
  sim$signal <- rep(sim$mu, sim$Lg); 
  sim$Name   <- paste0(gsub(",.*", "", sim$Name), ", x", alpha, ", K=", sim$Ktrue, ", n=", length(sim$signal))
  return(sim)
}

Simu_Ext <- lapply(Simu, FUN=function(sim, alphas=c(1, 3, 10)){
  new_sim <- lapply(alphas, FUN=one_Extend_Simu_Lg, sim=sim)
  return(new_sim)
})

```

### Simulation

We now simulate a number (10) profile per dataset and store them in RData.
```{r simulation_save}
set.seed(100)
storeSim <- function(sim, type.error, ns=nb_simu_per_dataset){
  file_sim <- paste0("Simu_Profile/Error=", type.error, "_", gsub(",[ ]", "_", sim$Name), ".RData")
  ## generate dataset if not already done
  if(!file.exists(file_sim)){
    data_sim <- replicate(ns, rSimu(sim, type.error=type.error))
    save(data_sim, file=file_sim, compress = TRUE)
  }
}

## This is about 110 Mo for alpha 1, 3, 100 and one type of error
for(type.error in type.errors){
for(sim_ext in Simu_Ext){
  lapply(sim_ext, FUN=storeSim, type.error=type.error)
}}

```


### Prior scaling 

Before we analyze any profile with any given segmentation method we scale it using
a differenced-based estimation of the variance (relying on the MAD).
The code is below.

```{r normalize_variance}
varDiff <- function(x, method='MAD'){
  n = length(x)
  if(method == "MAD"){
	return(mad(diff(x)/sqrt(2)))	
  }
  if(method == "HALL"){
    wei <- c(0.1942, 0.2809, 0.3832, -0.8582)
    mat <- wei %*% t(x)
    mat[2, -n] = mat[2, -1]
    mat[3, -c(n-1, n)] = mat[3, -c(1, 2)]
    mat[4, -c(n-2, n-1, n)] = mat[4, -c(1, 2, 3)]   
    return(sqrt(sum(apply(mat[, -c(n-2, n-1, n)], 2, sum)^2) / (n-3)))
  }
}

```

## Segmentation Approaches

We provide some code for various segmentation approaches.

```{r}
Seg.method <- list()
i <- 0
```



### PELT

#### PELT default

```{r PELT_Default_MBIC}
i <- i+1
library(changepoint)
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "Plt-Def"
Seg.method[[i]]$FUN <- function(x){
  w <- cpt.mean(x,method="PELT")
  w.cpt <- c(cpts(w), length(x))
     
  return(list(cpt=w.cpt))
}

```

#### PELT mBIC

```{r PELT_MBIC}
i <- i+1
library(changepoint)
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "Plt-Mbic"
Seg.method[[i]]$FUN <- function(x){
    sumstat<-matrix(c(cumsum(c(0,x)),cumsum(c(0,x^2)),cumsum(c(0,(x-mean(x))^2))),ncol=3)
    w<-PELT(sumstat,pen=2*log(length(x)),cost_func="mean.norm.mbic")
    return(list(cpt=w$cpts))   
}
```



```


### FPOP

#### FPOP-2log(n)
```{r FPOP_default}
i <- i+1
library(fpop)
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "Fpop-Def"
Seg.method[[i]]$FUN <- function(x){
  penalty <- 2*log(length(x))
  res <- Fpop(x, lambda=penalty)
  return( list(cpt=res$t.est) )
}

```

#### RFPOP-2log(n)
```{r RFPOP_default}
i <- i+1
library(robseg)
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "RFpop-Def"
Seg.method[[i]]$FUN <- function(x){
  penalty <- 2*log(length(x))
  res <- Rob_seg.std(x, loss="Outlier", lambda=penalty, lthreshold = 3)
  return( list(cpt=res$t.est) )
}

```


#### FPOP-CROPS-Cap

```{r FPOP_CROPS-Cap}

i <- i+1
source("CROPs.R")
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "Fpop-Cr-Cp"
Seg.method[[i]]$FUN <- function(x){
  n <- length(x)
  res <- CROPS.FPOP(x, min= 1/10*log(length(x)) ,max=10*log(length(x)))
  ## Capushe needs at least 10 models...
  dataCapushe <- data.frame(name=res[[1]][3,],
              pen.shape=lchoose(n-1,res[[1]][3,]),
              complexity=res[[1]][3,], contrast=res[[1]][4,])
  dataCapushe <- dataCapushe[(res[[1]][3,] <= (n/2 -3)), ]            
              
  KC <- try(DDSE(dataCapushe))
  KJ <- Djump(dataCapushe)
  if(class(KC) == "try-error"){ K <- as.integer(KJ@model) } else { K <- as.integer(KC@model) }
  index=(1:dim(res[[1]])[2])[res[[1]][3,]==K]
  
  return( list(cpt=res[[2]][[index]]) )
}

```

### FDRseg


#### Smuce default

```{r SmuceR_Default}

i <- i+1
library(FDRSeg)
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "FDRS-Smu"
Seg.method[[i]]$FUN <- function(x){
   if(length(x) <= 8000){
  res <- smuce(x)
  cpt <- c(res$left[-1]-1, length(x))
  return( list(cpt=cpt) ) } else {
  return( list(cpt=length(x)) )  }
}

```

#### FDRSeg Default

Not that for now we run FDRseg up $n=4000$.
For longer profiles is to slow for the debugging phase.
For longer profiles we simply output a 1 segment segmentation.

```{r FDRSeg_Default}
## as fdrseg is sometimes a bit long
## for the draft version only small profiles (less than 2000 datapoints)
## are analysed
i <- i+1
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "FDRS-Def"
Seg.method[[i]]$FUN <- function(x){
  if(length(x) <= 4000){
  res <- fdrseg(x)
  cpt <- c(res$left[-1]-1, length(x))
  return( list(cpt=cpt) )
  } else {
  return( list(cpt=length(x)) )  
  }
}

```


#### FDRSeg alpha=0.01



```{r FDRSeg_001}

#i <- i+1
#Seg.method[[i]] <- list()
#Seg.method[[i]]$Name <- "FDRS-0.01"
#Seg.method[[i]]$FUN <- function(x){
#  res <- fdrseg(x, alpha=0.01)
#  cpt <- c(res$left[-1]-1, length(x))
#  return( list(cpt=cpt) )

#}

```

### pDPA/Fpsn + Capushe

#### Fpsn Kmax=100

```{r pDPA_Capushe_100}
i <- i+1
library(jointseg)
library(capushe)
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "Fpsn-100"
Seg.method[[i]]$FUN <- function(x){
  Kmax <- min(trunc(length(x)/3), 100)
  res <- Fpsn(x, Kmax=Kmax)
  n <- length(x)
  dataCapushe <- data.frame(name=1:Kmax, 
              pen.shape=lchoose(n-1,0:(Kmax-1)), 
              complexity=1:Kmax, contrast=res$J.est)
  KC <- try(DDSE(dataCapushe))
  KJ <- Djump(dataCapushe)
  if(class(KC) == "try-error"){ K <- as.integer(KJ@model) } else { K <- as.integer(KC@model) }
 
  return( list(cpt=res$t.est[K, 1:K]) )
}

```

#### Fpsn Kmax=400

```{r pDPA_Capushe_400}
i <- i+1
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "Fpsn-400"
Seg.method[[i]]$FUN <- function(x){
  Kmax <- min(trunc(length(x)/3 ), 400)
  res <- Fpsn(x, Kmax=Kmax)
  n <- length(x)
  dataCapushe <- data.frame(name=1:Kmax,
            pen.shape=lchoose(n-1,0:(Kmax-1)), 
            complexity=1:Kmax, contrast=res$J.est)
  
  KC <- try(DDSE(dataCapushe))
  KJ <- Djump(dataCapushe)
  if(class(KC) == "try-error"){ K <- as.integer(KJ@model) } else { K <- as.integer(KC@model) }
 
  return( list(cpt=res$t.est[K, 1:K]) )
}

```

#### Fpsn Kmax=5\sqrt(n)

```{r pDPA_Capushe_sqr}
i <- i+1
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "Fpsn-sqr"
Seg.method[[i]]$FUN <- function(x){
  Kmax <- min(trunc(length(x)/3 ), trunc(5*sqrt(length(x))) )
  res <- Fpsn(x, Kmax=Kmax)
  n <- length(x)
  dataCapushe <- data.frame(name=1:Kmax,
            pen.shape=lchoose(n-1,0:(Kmax-1)), 
            complexity=1:Kmax, contrast=res$J.est)
  
  KC <- try(DDSE(dataCapushe))
  KJ <- Djump(dataCapushe)
  if(class(KC) == "try-error"){ K <- as.integer(KJ@model) } else { K <- as.integer(KC@model) }
 
  return( list(cpt=res$t.est[K, 1:K]) )
}

```




### Segmentor 

#### Kmax=100 

```{r Seg_Default}

i <- i+1
library(Segmentor3IsBack)
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "S3I-100"
Seg.method[[i]]$FUN <- function(x){
  res <- Segmentor(x, model=2, Kmax=100)
  K <- SelectModel(res)
  cpt <- res@breaks[K, 1:K]
  return( list(cpt=cpt) )
}

```

### Breakfast

#### TGUH

```{r Tguh_default}
i <- i+1
library(breakfast)
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "Bft-Tgu"
Seg.method[[i]]$FUN <- function(x){
  w <- tguh.cpt(x)
  w.cpt <- c(sort(w$cpt), length(x))
  return(list(cpt=w.cpt))
}

```

#### Hybrid approach
```{r Hybrid_default}
i <- i+1
library(breakfast)
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "Bft-Hyb"
Seg.method[[i]]$FUN <- function(x){
  w <- hybrid.cpt(x)
  w.cpt <- c(sort(w$cpt), length(x))
  return(list(cpt=w.cpt))
}

```

#### WBS 
```{r wbs_breakfast}
i <- i+1
library(breakfast)
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "Bft-Wbs"
Seg.method[[i]]$FUN <- function(x){
  w <- wbs.cpt(x)
  w.cpt <- c(sort(w$cpt), length(x))
  return(list(cpt=w.cpt))
}

```

### WBS

#### WBS-sSIC
```{r wbs_ssic}
library(wbs)
i <- i+1
library(breakfast)
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "Wbs-Ssic"
Seg.method[[i]]$FUN <- function(x){
     w <- wbs(x)
     w.cpt <- changepoints(w, penalty="ssic.penalty")
     w.cpt <- w.cpt$cpt.ic$ssic.penalty
     if(is.na(w.cpt[1])) w.cpt <- c() else { w.cpt <- sort(w.cpt)}

     return( list( cpt=c(w.cpt, length(x)) ) )
}

```


#### WBS-Threshold
```{r wbs_thres_1}
library(wbs)
i <- i+1
library(breakfast)
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "Wbs-Th1"
Seg.method[[i]]$FUN <- function(x){
     w <- wbs(x)
     w.cpt <- changepoints(w)
     w.cpt <- w.cpt$cpt.th[[1]]
     if(is.na(w.cpt[1])) w.cpt <- c() else { w.cpt <- sort(w.cpt)}
   return( list( cpt=c(w.cpt, length(x)) ) )
}

```

#### SBS-Threshold
```{r sbs_thres_1}
library(wbs)
i <- i+1
library(breakfast)
Seg.method[[i]] <- list()
Seg.method[[i]]$Name <- "Sbs-Th1"
Seg.method[[i]]$FUN <- function(x){
     w <- sbs(x)
     w.cpt <- changepoints(w)
     w.cpt <- w.cpt$cpt.th[[1]]
     if(is.na(w.cpt[1])) w.cpt <- c() else { w.cpt <- sort(w.cpt)}
   return( list( cpt=c(w.cpt, length(x)) ) )
}

```

## Assesment measure

We first define a set of functions to recover:

- the true number of segments
- the true segment of each datapoints
- the true signal

```{r trueSmt}
############################
trueK <- function(sim){
  return(sim$Ktrue)
}
############################
trueSeg <- function(sim){
  rep(1:length(sim$mu), sim$Lg)
}
############################
trueSmt <- function(sim){
  rep(sim$mu, sim$Lg)
}

```

We then define a set of functions to recover:

- the estimated number of segments
- the estimated segment of each datapoints
- the estimated signal

```{r predictedSmt}
predictedK <- function(fit, x){
  length(fit$cpt)
}

predictedSeg <- function(fit, x){
  lgSeg <- diff(c(0, sort(fit$cpt)))
  segNb <- rep(1:length(lgSeg), lgSeg)
  return(segNb)
}

predictedSmt <- function(fit, x){
  lgSeg <- diff(c(0, sort(fit$cpt)))
  segNb <- rep(1:length(lgSeg), lgSeg)
  smt <- rep(by(x, segNb, FUN=mean)[1:length(lgSeg)], lgSeg)
  return(smt)
}
```

### Number of segments

We consider three simple statistics to assess whether
any given method is able to recover the true number of segments:

- selD: $\hat{K}-K^*$
- selE: $\mathbb{I}_{\hat{K}=K^*}$
- selMs: $\mathbb{I}_{\hat{K}<K^*}$
- selPs: $\mathbb{I}_{\hat{K}>K^*}$

```{r Khat}
#########################################################
selD <- function(sim, fit, x){
  sc <- predictedK(fit, x) - trueK(sim)
  names(sc) <- "selD"
  return(sc)
}
#########################################################
selE <- function(sim, fit, x){
  sc <- predictedK(fit, x) == trueK(sim)
  names(sc) <- "selE"
  return(sc)
}
#########################################################
selMs <- function(sim, fit, x){
  sc <- predictedK(fit, x) < trueK(sim)
  names(sc) <- "selMs"
  return(sc)
}
#########################################################
selPs <- function(sim, fit, x){
  sc <- predictedK(fit, x) > trueK(sim)
  names(sc) <- "selPs"
  return(sc)
}

```

### Mean-squared Error 

Here is a function to compute the MSE and the MSE divided by the MSE
obtained when considering only 1 segment (MSE_N).

```{r MSE}
#########################################################
MSE <- function(sim, fit, x){
  sc <- mean(  (trueSmt(sim) - predictedSmt(fit, x))^2  )
  names(sc) <- "Mse"
  return(sc)
}
#########################################################
MSE_N <- function(sim, fit, x){
  sc   <- mean(  (trueSmt(sim) - predictedSmt(fit, x))^2  )
  sc_n <- mean(  (      x     -      mean(x)         )^2  )
  sc <- sc/sc_n
  names(sc) <- "Mse_N"
  return(sc)
}
```

### Segmentation scoring

#### NID

Here is a function to compute the NID (Normalize Information distance) between the true and estimated segmentation. A score 
of 0 means a perfect match between the two.

```{r nid_score}
library(aricode)
nidScore <- function(sim, fit, x){
  if(trueK(sim) > 1){
    sc <- NID(trueSeg(sim), predictedSeg(fit, x))
  } else {
    sc <- NA
  }
  names(sc) <- "Nid"
  return(sc)
}

```

#### ARI
Here is a function to compute the ARI between the true and estimated segmentation. A score of 1 means a perfect match between the true
and estimated segmentation.

```{r ari_score}
ariScore <- function(sim, fit, x){
  if(trueK(sim) > 1){
    sc <- ARI(trueSeg(sim), predictedSeg(fit, x))
  } else {
    sc <- NA
  }
  names(sc) <- "Ari"
  return(sc)
}
```

#### Froebenius norm 
Here is a function to compute the Froebenius norm between the true and estimated segmentation. 

```{r Fb_score}
froebScore <- function(sim, fit, x){
   
 truesegment <- trueSeg(sim)
 predsegment     <- predictedSeg(fit, x)
 lseg        <- diff(c(0, fit$cpt))
 i_order <- order(truesegment, predsegment, method = "radix") - 1L
 #contingency <- table(truesegment, predsegment)
 contingency <- sortPairs(truesegment, predsegment, spMat=TRUE)$spMat 
 mattruesegment <- matrix(rep(sim$Lg, length(lseg)), ncol=length(lseg), byrow=FALSE)
 matsegment <- matrix(rep(lseg, length(sim$Lg)), nrow=length(sim$Lg), byrow=TRUE)

 
 part_Diff <- sum( contingency^2 * (1/mattruesegment - 1/matsegment)^2)
 part_Zero_truesegment <-  trueK(sim) - sum( contingency^2 * (1/mattruesegment)^2)
 part_Zero_segment <-predictedK(fit, x) - sum( contingency^2 * (1/matsegment)^2)

 sc <- sqrt(part_Diff+part_Zero_truesegment+part_Zero_segment)
  
 
 names(sc) <- "Fb"
 return(sc)
}
```



### List of all scoring functions

We make a list of all these scoring functions.

```{r all_scores}
Score.fun <- list()
i <- 1
Score.fun[[i]] <- MSE            ; i <- i+1
Score.fun[[i]] <- MSE_N          ; i <- i+1
Score.fun[[i]] <- selE           ; i <- i+1
Score.fun[[i]] <- froebScore     ; i <- i+1

Score.fun[[i]] <- selD           ; i <- i+1
Score.fun[[i]] <- selMs          ; i <- i+1
Score.fun[[i]] <- selPs          ; i <- i+1
Score.fun[[i]] <- nidScore       ; i <- i+1
Score.fun[[i]] <- ariScore       ; i <- i+1

```

## Segmentation and scoring


### Segmentation
We run all approches and assess their performances.


```{r load_simu_and_seg}
## Basics all ~ 4h30 with mc.cores=4
library(parallel)
one_simu_seg <- function(sim, method, type.error){
  file_sim <- paste0("Simu_Profile/Error=", type.error, "_", gsub(",[ ]", "_", sim$Name), ".RData")
  file_seg <- paste0("Seg_Approach/Error=", type.error, "_", gsub(",[ ]", "_", sim$Name),  "_", method$Name, ".RData")

  ## run the approach only if not run already
  if(file.exists(file_sim)){
  if(!file.exists(file_seg)){
    load(file=file_sim)
    output.met <- mclapply(1:ncol(data_sim), FUN=function(i){
      x_ <- data_sim[, i]/varDiff(data_sim[, i])
      runtime <- system.time(res <- method$FUN(x_))[3]
      return(list(res=res, runtime=runtime))
      }, mc.cores=mc.cores)
  
    save(output.met, file=file_seg)
  
  }} else {cat("Generate simulation dataset first")}
}

###  
for(type.error in type.errors){
  for(sim_ext in Simu_Ext){
    for(met in Seg.method){
      lapply(sim_ext, FUN=one_simu_seg, method=met, type.error=type.error)
}}}

```


### Scoring
```{r load_seg_and_score}

one_simu_score <- function(sim, method, type.error, Score.fun_){
  file_sim <- paste0("Simu_Profile/Error=", type.error, "_", gsub(",[ ]", "_", sim$Name), ".RData")
  file_seg <- paste0("Seg_Approach/Error=", type.error, "_", gsub(",[ ]", "_", sim$Name),  "_", method$Name, ".RData")
  file_sco <- paste0("Sco_Approach/Error=", type.error, "_", gsub(",[ ]", "_", sim$Name),  "_", method$Name, ".RData")
  ## run the approach only if not run already
  if(file.exists(file_seg)){
  if(!file.exists(file_sco)){
    load(file=file_seg)
    load(file=file_sim)
    
    output.sco <- do.call(rbind, 
        mclapply(1:length(output.met), FUN=function(i){
          x <- c(i, output.met[[i]]$runtime, sapply(Score.fun_, FUN=function(fun) 
                fun(sim=sim, fit=output.met[[i]]$res, x=data_sim[, i])))
         
          names(x)[1:2] <- c("sim_num", "t")
          return(x)
        }, mc.cores=mc.cores) 
    )
    
    save(output.sco, file=file_sco)
  
  }} else {cat("Run segmentation first")}
}


##


## 
for(type.error in type.errors){
  for(sim_ext in Simu_Ext){
    for(met in Seg.method){
      lapply(sim_ext, FUN=one_simu_score, method=met, type.error=type.error, Score.fun_=Score.fun)
    }}}

```

### Summarized results

#### Gaussian errors

```{r table_summarization_gauss, results='asis'}
library(knitr)
library(kableExtra)

one_load_aggregate <- function(sim, method, type.error){
  file_sco <- paste0("Sco_Approach/Error=", type.error, "_", gsub(",[ ]", "_", sim$Name),  "_", method$Name, ".RData")
  load(file_sco)
  data.frame(met=method$Name, t(signif(colMeans(output.sco[, c(2, 3, 5)]),2)))
}

all_load_aggregate <- function(sim, Seg.method_, type.error){
  do.call(rbind, lapply(Seg.method_, FUN=function(met) one_load_aggregate(sim=sim, method=met, type.erro=type.error)))
}

#sim <- Simu_Ext[[3]][[1]]
#i <- 7
#while(i <= 12) {
#  one_load_aggregate(Simu_Ext[[i]][[1]], Seg.method[[5]], "Gauss")
#  i <- i+1
#}

type.error <- "Gauss"
for(sim_ext in Simu_Ext){
    nb_lg <- length(sim_ext)
    data_to_show <- lapply(sim_ext, FUN=function(sim) all_load_aggregate(sim, Seg.method_=Seg.method, type.error=type.error))
    nb_so <- ncol(data_to_show[[1]])
    icol <- rep(2:nb_so, each=nb_lg) + ((1:nb_lg) -1)*nb_so
    subname <- sapply(sim_ext, FUN=function(sim) paste0("_(x", gsub(".*x|,.*", "", sim$Name), ")"))
    for(i in 1:length(sim_ext)){
      colnames(data_to_show[[i]]) <- paste0(colnames(data_to_show[[i]]), subname[i])
    }
    data_to_show <- do.call(cbind, data_to_show)[, c(1, icol)]
    colnames(data_to_show)[1] <- "Met"

     essai <- kable(data_to_show, row.names = FALSE,  align="c", format="html", caption=paste0(sim_ext[[1]]$Name, ", Gauss") ) %>%
              kable_styling(bootstrap_options = c("hover", "striped")) %>%
              add_header_above(c(" " = 1, "Time" = nb_lg, "MSE" = nb_lg, "E(K=K*)" = nb_lg)) %>%
              column_spec((1:nb_lg-1)*nb_lg+1, border_right = T) %>%
             row_spec(c(7, 12, 14), bold = T, color = "white", background = "#D7261E")
     print(essai)
  }
    
```

#### Student error
```{r table_summarization_stu-10, results='asis'}
type.error <- "Stud-10"
for(sim_ext in Simu_Ext){

    #print(sim$Name)
    
    nb_lg <- length(sim_ext)
    data_to_show <- lapply(sim_ext, FUN=function(sim) all_load_aggregate(sim, Seg.method_=Seg.method, type.error=type.error))
    nb_so <- ncol(data_to_show[[1]])
    icol <- rep(2:nb_so, each=nb_lg) + ((1:nb_lg) -1)*nb_so
    subname <- sapply(sim_ext, FUN=function(sim) paste0("_(x", gsub(".*x|,.*", "", sim$Name), ")"))
    for(i in 1:length(sim_ext)){
      colnames(data_to_show[[i]]) <- paste0(colnames(data_to_show[[i]]), subname[i])
    }
    data_to_show <- do.call(cbind, data_to_show)[, c(1, icol)]
    colnames(data_to_show)[1] <- "Met"
  
  
    essai <- kable(data_to_show, row.names = FALSE,  align="c", format="html", caption=paste0(sim_ext[[1]]$Name, ", Student df=10")) %>% 
             kable_styling(bootstrap_options = c("hover")) %>%
             add_header_above(c(" " = 1, "Time" = nb_lg, "MSE" = nb_lg, "E(K=K*)" = nb_lg)) %>%
             column_spec((1:nb_lg-1)*nb_lg+1, border_right = T) %>%
             row_spec(c(7, 12, 14), bold = T, color = "white", background = "#D7261E")
    print(essai)
  }
    
```
    
### Plots
